---
title: "Viz1"
author: "Austin Hsin"
date: "2023-09-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
```

## NOAA Weather dataset import

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Molokai_HI",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())

weather_df
```

## Basic Scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()

```

ggp_weather = 
  weather_df |>
  ggplot(aes(x = tmin, y = tmax)) 

ggp_weather + geom_point()

*Note that you can pipe from the dataframe to make a plot and save it 

## Advanced Scatterplot
```{r}
# Adding color through the names and adding a smooth line
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  geom_smooth(se = FALSE)

# Separating plots via facet
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)

# Sizing by precipitation
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

## Learning Assessment
```{r}
weather_df |>
  filter(name == "CentralPark_NY")|>
  mutate(
    tmax_fahr = tmax * (9 / 5) + 32,
    tmin_fahr = tmin * (9 / 5) + 32) |> 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", se = FALSE)
```

*Note: data frame - filters specific column, mutates temp min max variables from celsius to fahrenheit then plots min fahr by max fahr

## Other plots
```{r}
# Smooth Lines only
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_smooth(se = FALSE) 

# 'geom_hex' (and noting 'geom_bin2d' and 'geom_density2d')
ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_hex()
```

## Learning Assessment
```{r}
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin), color = "blue")
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin, color = "blue"))
```

In the first attempt, we’re defining the color of the points by hand; in the second attempt, we’re implicitly creating a color variable that has the value blue everywhere; ggplot is then assigning colors according to this variable using the default color scheme.

## Univariate Plot
```{r}
ggplot(weather_df, aes(x = tmax)) + 
  geom_histogram()

ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram(position = "dodge", binwidth = 2)

ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")

ggplot(weather_df, aes(x = name, y = tmax)) + geom_boxplot()

ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), alpha = .5) + 
  stat_summary(fun = "median", color = "blue")

ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)

weather_plot = ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) 

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)
```
